Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-15 WSSSPE2_report/WSSSPE2_review.tex
alphabetize attendees

\todo{VOLUNTEER NEEDED to neaten this - alphabetize by surname, columnize, add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

Alice Allen, Astrophysics Source Code Library (ASCL)
David Bernholdt, Oak Ridge National Laboratory
Jakob Blomer
Carl Boettiger, UCSC/ropensci
Chris Bogart, ISR/CMU
Dirk Colbry, Michigan State University
Anshu Dubey, Lawrence Berkeley National Laboratory
David Henty,  EPCC, The University of Edinburgh
Maxime Hughes
Eric Hutton,  University of Colorado
Daniel S. Katz, U Chicago \& Argonne
Ian Kelley 
Chris Lenhardt
Andre Luckow, Rutgers
Berkin Malkoc, Istanbul Technical University
Bryan Marker, The University of Texas at Austin
Rupert Nash
Andy Nutter-Upham, Whitehead Institute
Abani Patra, Univ @ Buffalo
Aleksandra Pawlik, Software Sustainability Institute
Cody J. Permann, Idaho National Laboratory
Benjamin Pharr, University of Mississippi
Mike Rilee
Erin Robinson, Foundation for Earth Science 
Alan Simpson,  EPCC, The University of Edinburgh
Justin Shi
Ardita Shkurti, University of Nottingham
Carol Song, Purdue University
Colin C. Venters, University of Huddersfield
Nathan Weeks
Ethan White, University of Florida/Utah State University
Ethan Davis, UCAR Unidata
Frank L\"{o}ffler, Louisiana State University
Frank Seinstra, Netherlands eScience Center
Gabrielle Allen, U Illinois
Greg Wilson,  Software Carpentry
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University
James Howison, University of Texas
James Shepherd, Rice University
James Spencer, Imperial College London
John W. Cobb
John W. Peterson, Idaho National Laboratory
Jordan Adams, Tulane University
Jory Schossau, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab
Karen Cranston, NESCent
Karthik Ram, University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Kurt Glaesemann, Pacific northwest national lab
Kyle Marcus, University of Buffalo
Marcus D. Hanwell, Kitware
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Marlon Pierce, Indiana University
Matt Jones,  University of California Santa Barbara
Matt Turk, NCSA/UIUC
Mike Rilee, NASA/GSFC, Rilee Systems Technologies - 
Nancy Wilkins-Diehr, SDSC
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh
Nick Jones, New Zealand eScience Infrastructure, University of Auckland
Nicole Gasparini, Tulane University, New Orleans
Pierre-Yves Aquilanti, TOTAL E\&P R\&T USA
Ray Idaszak, RENCI/UNC
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Richard Littauer, MIT/University of Saarland 
Robert H. McDonald, Indiana University - Data to Insight Center/Libraries - 
Robert R Downs, CIESIN, Columbia University
Samin Ishtiaq, Microsoft Research Cambridge, UK
Sarah Harris, University of Leeds
Sol Greenspan,  National Science Foundation
Stephen Piccolo,  Brigham Young University, Utah
Steven R. Brandt, Louisiana State University
Suresh Marru, Indiana University 
Sushil Prasad, Georgia State University, Atlanta 
Ted Habermann, The HDF Group
Tom Clune, NASA GSFC - 
Tom Crick, Cardiff Metropolitan University, UK
Tracy Teal, Data Carpentry
Wolfgang Bangerth
Yolanda Gil, Information Sciences Institute, University of Southern California

>>>>

\todo{VOLUNTEER NEEDED to neaten this - columnize, add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

Jordan Adams, Tulane University
Alice Allen, Astrophysics Source Code Library (ASCL)
Gabrielle Allen, U Illinois
Pierre-Yves Aquilanti, TOTAL E\&P R\&T USA
Wolfgang Bangerth
David Bernholdt, Oak Ridge National Laboratory
Jakob Blomer
Carl Boettiger, UCSC/ropensci
Chris Bogart, ISR/CMU
Steven R. Brandt, Louisiana State University
Tom Clune, NASA GSFC - 
John W. Cobb
Dirk Colbry, Michigan State University
Karen Cranston, NESCent
Tom Crick, Cardiff Metropolitan University, UK
Ethan Davis, UCAR Unidata
Robert R Downs, CIESIN, Columbia University
Anshu Dubey, Lawrence Berkeley National Laboratory
Nicole Gasparini, Tulane University, New Orleans
Yolanda Gil, Information Sciences Institute, University of Southern California
Kurt Glaesemann, Pacific northwest national lab
Sol Greenspan,  National Science Foundation
Ted Habermann, The HDF Group
Marcus D. Hanwell, Kitware
Sarah Harris, University of Leeds
David Henty,  EPCC, The University of Edinburgh
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh
James Howison, University of Texas
Maxime Hughes
Eric Hutton,  University of Colorado
Ray Idaszak, RENCI/UNC
Samin Ishtiaq, Microsoft Research Cambridge, UK
Matt Jones,  University of California Santa Barbara
Nick Jones, New Zealand eScience Infrastructure, University of Auckland
Daniel S. Katz, U Chicago \& Argonne
Ian Kelley
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University
Chris Lenhardt
Richard Littauer, MIT/University of Saarland 
Frank L\"{o}ffler, Louisiana State University
Andre Luckow, Rutgers
Berkin Malkoc, Istanbul Technical University
Kyle Marcus, University of Buffalo
Bryan Marker, The University of Texas at Austin
Suresh Marru, Indiana University 
Robert H. McDonald, Indiana University - Data to Insight Center/Libraries - 
Rupert Nash
Andy Nutter-Upham, Whitehead Institute
Abani Patra, Univ @ Buffalo
Aleksandra Pawlik, Software Sustainability Institute
Cody J. Permann, Idaho National Laboratory
John W. Peterson, Idaho National Laboratory
Benjamin Pharr, University of Mississippi
Stephen Piccolo,  Brigham Young University, Utah
Marlon Pierce, Indiana University
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Sushil Prasad, Georgia State University, Atlanta 
Karthik Ram, University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Mike Rilee
Mike Rilee, NASA/GSFC, Rilee Systems Technologies - 
Erin Robinson, Foundation for Earth Science 
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Jory Schossau, Michigan State University
Frank Seinstra, Netherlands eScience Center
James Shepherd, Rice University
Justin Shi
Ardita Shkurti, University of Nottingham
Alan Simpson,  EPCC, The University of Edinburgh
Carol Song, Purdue University
James Spencer, Imperial College London
Tracy Teal, Data Carpentry
Kaitlin Thaney,  Mozilla Science Lab
Matt Turk, NCSA/UIUC
Colin C. Venters, University of Huddersfield
Nathan Weeks
Ethan White, University of Florida/Utah State University
Nancy Wilkins-Diehr, SDSC
Greg Wilson,  Software Carpentry
